Bus lines, multilines approach

### 2022-03-29 multiple_lines/notes/latex/Notes_trajet.tex
Multiple lines notes updated

\subsection{Problem definition}

Suppose that we possess two $n$-length vectors $\mathbf{x}_\text{in} = (x^\text{in}_i)$ and $\mathbf{y}_\text{out} = (y^\text{out}_i)$, representing respectively the flow entering the network at stop $i$ and going out of the network at stop $i$.

\end{document}

>>>>

\subsection{Flow definition}

A matrix $\mathbf{N} = (n_{ij})$, verifying:
\begin{enumerate}
	\item $n_{ij} \geq 0$
	\item $a_{ij} = 0 \Rightarrow n_{ij} = 0$
\end{enumerate}
is a \emph{flow matrix} defined on $\mathcal{G}$. Again, we can decompose this matrix with 
\begin{equation}
\mathbf{N} = \mathbf{N}_\text{W} + \mathbf{N}_\text{B} \qquad \mathbf{N}_\text{W} := \sum_{k=1}^l \mathbf{N}_k
\end{equation}
where the flow $\mathbf{N}_\text{W}$ is the flow inside the lines, $\mathbf{N}_\text{B}$ the flow between lines, and $\mathbf{N}_l$ the flow inside line $l$.

Suppose that we possess two $n$-length vectors $\mathbf{l}_\text{in} = (l^\text{in}_i)$ and $\mathbf{l}_\text{out} = (l^\text{out}_i)$, representing ,respectively, the flow entering the line associated with stop $i$ and going out of this line at stop $i$. These vectors can in fact be expressed with: 
\begin{align}
\mathbf{l}_\text{in} &= \bm{\sigma}_\text{in} + 
\end{align}
\end{document}
